### 2015-04-18 usecase-policy.tex

\subsection{Package Views}
\label{sec:package-views}

@@

\subsection{Package Configurations}

It is also useful to specify site-specific options for how packages should be built.  The correct configure line for building packages may be different across sites.  For example, the Spindle tool can have logging locations and security policies specified on its configure line.  Spack can make reasonable guesses about Spindle's proper configure line, but it cannot create a customized installation for the site.  One way to solve this would be to edit the Spindle package description in Spack and manually change how configure is invoked.  This is not ideal, as the Spindle package description is part of the Spack source code, and modifying it makes it difficult to share Spack versions and updates across sites.

Instead Spack allows the creation of site-specific variants of packages.  The build instructions for a Spack package are encoded in a Python class, which must inherit from Spack's {\tt Package} class.  Via the {\tt spackconfig} file, users can specify additional search directories for finding additional {\tt Package} classes.  These additional packages can inherit from and replace the Spack's default packages, allowing sites to either tweak or completely replace Spack's build recipes.  To continue the previous example, a site can write a {\tt LocalSpindle} Python class, which inherits from Spack's {\tt Spindle} class.  {\tt LocalSpindle} may simply add additional configure flags to the {\tt Spindle} class, while leaving the dependencies and most of the build instructions from its parent class.  To keep builds deterministic and reproducable, Spack also tracks which {\tt Package} class drove a specific build.

>>>>

\subsubsection{Package Views}
\label{sec:package-views}

@@

By default, Spack stores its package files in a mainline repository that is present when users
first run Spack.  At many sites, packages may build sensitive, proprietary software, or they 
may have patches that are not useful outside of a certain company or organization.  Putting
this type of code back into a public repository does not often make sense, and if it makes the
mainline less stable, it can actually make sharing code between sites more difficult.

To support our own private packages, and to support those of LLNL code teams, Spack allows he creation of site-specific variants of packages.

The build instructions for a Spack package are encoded in a Python class, which must inherit from Spack's {\tt Package} class.  Via the {\tt spackconfig} file, users can specify additional search directories for finding additional {\tt Package} classes.  These additional packages can inherit from and replace the Spack's default packages, allowing sites to either tweak or completely replace Spack's build recipes.  To continue the previous example, a site can write a {\tt LocalSpindle} Python class, which inherits from Spack's {\tt Spindle} class.  {\tt LocalSpindle} may simply add additional configure flags to the {\tt Spindle} class, while leaving the dependencies and most of the build instructions from its parent class.  To keep builds deterministic and reproducable, Spack also tracks which {\tt Package} class drove a specific build.
